{\scshape Denicek}: Computational Substrate for Concrete, \\Collaborative, Interactive Programming

### 2024-11-02 paper.tex
Intro to implementation

\documentclass[sigconf]{acmart}
%\documentclass[sigconf,review,anonymous]{acmart}

@@

\begin{document}
\title[Denicek: Programming Substrate for Concrete, Collaborative, Interactive
  Programming]{{\scshape Denicek}: Programming Substrate for Concrete, \\Collaborative, Interactive Programming}

@@

\begin{abstract}
Research on interactive programming systems gave rise to a range of programming experiences,
including programming by demonstration, local-first collaborative editing, structure
editing, schema and code co-evolution, provenance tracking and output invalidation. Those
experiences are compelling, but they are hard to implement on the basis of existing programming
languages and systems.

@@

@@

\section{Implementation}
\label{sec:impl}
(how each of the features is achieved)

1) PBD (create textbox but not button)

2) Merging (refactoring)

@@

\subsection{Evaluation and invalidation}
\label{sec:impl-eval}

5) Schema evolution

>>>>

% TODO: Figure out how to call those "programming experiences" (also is this a good name?)
%   the text uses "concrete, collaborative, interactive" - but this is a silly list
%   really, they are "cool" but how to say that.
%
% TODO: Also, what exactly goes into the list?
%
%
\documentclass[sigconf]{acmart}
%\documentclass[sigconf,review,anonymous]{acmart}

@@

\begin{document}
\title[Denicek: Computational Substrate for Concrete, Collaborative, Interactive
  Programming]{{\scshape Denicek}: Computational Substrate for Concrete, \\Collaborative, Interactive Programming}

@@

\begin{abstract}
Research on interactive programming systems gave rise to a range of programming experiences,
including programming by demonstration, local-first collaborative editing, %structure editing,
schema and code co-evo\-lution, provenance tracking and incremental recomputation. Those
experiences are compelling, but they are hard to implement on the basis of existing programming
languages and systems.

@@

explain computational substrate

@@

\section{Implementation}
\label{sec:impl}

The key claim of this paper is that the computational substrate described in the previous
section makes it easy to support a range of experiences that make programming more concrete,
collaborative and interactive. In this section, we describe how to use the substrate to support
local-first collaborative editing (\S\ref{sec:impl-collab}), programming by
demonstration (\S\ref{sec:impl-pbd} and \S\ref{sec:impl-interaction}),
schema and code co-evolution (\S\ref{sec:impl-schema}), incremental recomputation
(\S\ref{sec:impl-eval}), provenance tracking (\S\ref{sec:impl-provenance})
and concrete programming via managed copy \& paste (\S\ref{sec:impl-copy}).
We describe the programming experience in isolation in this section. Next section provides a
more comprehensive evaluation through a case study that combines multiple of them together.

\subsection{Merging (refactoring)}
\label{sec:impl-collab}

\subsection{PBD (create textbox but not button)}
\label{sec:impl-pbd}

@@

\subsection{Schema code co-evolution}
\label{sec:impl-schema}

\subsection{Incremental recomputation}
\label{sec:impl-eval}

\subsection{Provenance tracking}
\label{sec:impl-provenance}

\subsection{Managed copy \& paste}
\label{sec:impl-copy}
